Tensor anisotropy as a tracer of cosmic voids

### 2015-05-26 cosmic_voids.tex
solved minor issue #20. replaced r_eff by r/r_eff

  \captionof{figure}{\small Left panel, void size distribution. Right
    panel, fraction of overcompensated/subcompensated ($C>1/C<1$)voids as a
    function of the effective radius. The continous (dashed)
    curves correspond to the T-Web (V-Web).
    The abundance for small ($r_{eff}<2.0\hMpc$) overcompensated voids
    shoots up in the V-Web scheme.
    We provide in the body of the paper two reasons for this behaviour.}
  \label{fig:volume_function}

@@

Comparing the abundance of large voids in the two web schemes, we find
that the largest voids in the V-Web have $r_{\rm eff}\sim 10$\hMpc,
while the T-Web scheme includes voids as large as $r_{\rm eff}\sim 15$\hMpc. 
This suggests that large voids in the T-Web scheme have a velocity
structure that splits them in the V-Web. 
This increased granularity in the velocity structure of voids is
evident in the left and right panels of Fig. \ref{fig:FA_field}.

@@

%.........................................................................
\begin{table}[!htbp]
\centering
\begin{tabular}{c | c c | c c}
\toprule
\multicolumn{1}{c}{}&  \multicolumn{2}{c}{\textbf{Tweb}} & \multicolumn{2}{c}{\textbf{Vweb}}\\
%\midrule
\textbf{${\bf r_{\rm eff}}$[\hMpc]}   & $\bf{C<1}$   & $\bf{C>1}$    & $\bf{C<1}$   & $\bf{C>1}$\\ \hline
%\midrule
$<2.0$        &  997 & 495   & 13480  & 711\\
$2.0-3.2$     &  791 & 471   & 2581   & 583\\
$3.2-4.4$     &  941 & 469   & 2168   & 656\\
$4.4-5.6$     &  869 & 467   & 1934   & 724\\
$5.6-6.8$     &  769 & 395   & 1287   & 584\\
$6.8-8.3$     &  665 & 362   & 700    & 315\\
$8.3-12.0$    &  587 & 333   & 123    & 61\\
$>12.0$       &  29  & 23    & 0      & 0\\ \hline
\textbf{total}& 5648 & 3015  & 22273  & 3634\\
\bottomrule
\end{tabular}
\caption{Number of voids for each bin of effective radius and for 
subcompensanted and overcompansated samples.}
\label{tab:number_voids}
\end{table}
%.........................................................................

@@

The first interesting result is the overdensity value at the void's
center.
We find that larger voids have a lower overdensity value.
The largest voids ($8.3-12\ \hMpc$) have an underdensity
$\sim-0.95$ while smaller voids  ($2-3.2\ \hMpc$) fall around $\delta\sim 
-0.8$ at their centers.
This holds for both web schemes. 
These values are consistent with most of the void finding schemes
based on smooth and continuous fields from simulation or
reconstruction procedures on surveys \citep{Plionis02, Colberg05,
  Shandarin06,  Platen07, Neyrinck08, MunozCuartas11, Ceccarelli13,
  Paz13, Neyrinck13, Ricciardelli2013}, unlike geometrical approaches based 
on point distributions, where central density values are generally higher
\citep{Colberg08}.

@@

All the previous results hold for both finding schemes.
This suggests an universal behaviour for the radial density profile in
two families of subcompensated and overcompensanted voids. 
This goes in the same direction of recent results about the internal
\citep{Colberg05,  Ricciardelli2013} and external structure of voids
\citep{Lavaux12, Ceccarelli13, Paz13, Hamaus14}. 
Our results extend the findings of \cite{Hamaus14} into the range of
voids with size $r_{\rm eff}<10$\hMpc.

@@

\before{We find that subcompensated voids have outflowing velocity profiles
all the way up to the effective radius where the average radial
density reaches the average value.}
\after{We find that subcompensated voids have outflowing velocity profiles
all the way up to the radius where the average radial
density reaches the average value.}
For voids with sizes $r_{\rm eff}<8\hMpc$ the outflow is always
positive, consistent with the fact that their density profiles do not
reach the level $\delta=0$ in the range of explored radii.
This behaviour indicates that matter is being pulled out of the void
into external higher density features.

@@

Fig. \ref{fig:FA_profile} shows the results for the FA profiles.
We find that the FA clearly magnifies the difference between the
internal profile $r_{\rm eff}<1$ and the external profile $r_{\rm
  eff}>1$. 
Subcompensanted voids in the T-Web reach an asymptotic background
value of F=$0.8$ almost right at $r_{\rm eff}=2$. 
For the V-Web the results are similar, albeit rather slowly with the
effective radius.
Overcompensated voids reach a maximum FA at the same effective radiuus
$r_{\rm eff}=1$ and decline to reach an asymptotic value of FA=$0.85$
at larger radii.

@@

The difference between the radius where the density ridge is reached 
($r_{\rm eff}=3$) and the radius of the FA  ridge ($r_{\rm eff}=1$ )
justifies in a more quantiative way the qualitative argument
we present in sub-section \ref{subsec:watershed} to define void boundaries in
our method.  
Namely that as we increase the void boundary, we reach
first middle density walls, before reaching high density structures
associated with high anisotropy. 
This makes the FA ridge a reasonable
boundary for voids compared to the traditional definition that puts
the boundary at the density ridge.

@@

For the density the most interesting feature is that the  profile has
a similar shape for all the different void sizes once the radial
coordinate is expressed in units of the effective radius.  
In these profiles it is evident the presence of an overdense ridge
around $2<r/r_{\rm eff}<3$ for the overcompensated voids.
Subcompensated voids do not show such a ridge keeping its density
lower than the average value up to $r/r_{\rm eff}\sim 8$.

In other studies where voids are found using considerations on the
density fields the ridge is, almost by definition, located around
$r/r_{\rm eff}\sim 1$ and the subcompensated voids reach average
density around $r/r_{\rm eff}\sim 3$. 
This indicates that voids defined by FA boundaries are smaller  than
voids found by density only considerations close by a radial factor of
$2$.

@@

The Fractional Anisotropy profiles also show remarkable similarities
inside each class of subcompensated and overcompensated voids
and a close correlation with the behaviour in the density and velocity
profiles. 
From these profiles it becomes clear that the limit of overcompensated
void coincides with a ridge in of FA values close to $0.9$. 
This value is close to the limit FA=$0.95$ we impose in the watershed
algorithm, indicating that these voids are very close to spherical.
For the subcompensated voids the FA quickly increases to FA values of 
$\sim 0.7-0.8$ at $r/r_{\rm eff}\sim 1$ to find a plateau, which is
quite far from the limiting FA$=0.95$ suggesting that these voids are
far from spherical.

>>>>

  \captionof{figure}{\small Left panel, void size distribution. Right
    panel, fraction of overcompensated/subcompensated ($C>1/C<1$)voids as a
    function of the effective radius. The continous (dashed)
    curves correspond to the T-Web (V-Web).
    The abundance for small ($\reff <2.0\hMpc$) overcompensated voids
    shoots up in the V-Web scheme.
    We provide in the body of the paper two reasons for this behaviour.}
  \label{fig:volume_function}

@@

Comparing the abundance of large voids in the two web schemes, we find
that the largest voids in the V-Web have $\reff \sim 10$\hMpc,
while the T-Web scheme includes voids as large as $\reff \sim 15$\hMpc. 
This suggests that large voids in the T-Web scheme have a velocity
structure that splits them in the V-Web. 
This increased granularity in the velocity structure of voids is
evident in the left and right panels of Fig. \ref{fig:FA_field}.

@@

%.........................................................................
\begin{table}[!htbp]
\centering
\begin{tabular}{c | c c | c c}
\toprule
\multicolumn{1}{c}{}&  \multicolumn{2}{c}{\textbf{Tweb}} & \multicolumn{2}{c}{\textbf{Vweb}}\\
%\midrule
\textbf{${\bf \reff }$[\hMpc]}   & $\bf{C<1}$   & $\bf{C>1}$    & $\bf{C<1}$   & $\bf{C>1}$\\ \hline
%\midrule
$<2.0$        &  997 & 495   & 13480  & 711\\
$2.0-3.2$     &  791 & 471   & 2581   & 583\\
$3.2-4.4$     &  941 & 469   & 2168   & 656\\
$4.4-5.6$     &  869 & 467   & 1934   & 724\\
$5.6-6.8$     &  769 & 395   & 1287   & 584\\
$6.8-8.3$     &  665 & 362   & 700    & 315\\
$8.3-12.0$    &  587 & 333   & 123    & 61\\
$>12.0$       &  29  & 23    & 0      & 0\\ \hline
\textbf{total}& 5648 & 3015  & 22273  & 3634\\
\bottomrule
\end{tabular}
\caption{Number of voids for each bin of effective radius and for 
subcompensanted and overcompansated samples.}
\label{tab:number_voids}
\end{table}
%.........................................................................

@@

The first interesting result is the overdensity value at the void's
center.
We find that larger voids have a lower overdensity value.
The largest voids ($8.3-12\ \hMpc$) have an underdensity
$\delta \sim-0.95$ while smaller voids  ($2-3.2\ \hMpc$) fall around $\delta\sim 
-0.8$ at their centers.
This holds for both web schemes. 
These values are consistent with most of the void finding schemes
based on smooth and continuous fields from simulation or
reconstruction procedures on surveys \citep{Plionis02, Colberg05,
  Shandarin06,  Platen07, Neyrinck08, MunozCuartas11, Ceccarelli13,
  Paz13, Neyrinck13, Ricciardelli2013}, unlike geometrical approaches based 
on point distributions, where central density values are generally higher
\citep{Colberg08}.

@@

All the previous results hold for both finding schemes.
This suggests an universal behaviour for the radial density profile in
two families of subcompensated and overcompensanted voids. 
This goes in the same direction of recent results about the internal
\citep{Colberg05,  Ricciardelli2013} and external structure of voids
\citep{Lavaux12, Ceccarelli13, Paz13, Hamaus14}. 
Our results extend the findings of \cite{Hamaus14} into the range of
voids with size $\reff <10$\hMpc.

@@

\before{We find that subcompensated voids have outflowing velocity profiles
all the way up to the effective radius where the average radial
density reaches the average value.}
\after{We find that subcompensated voids have outflowing velocity profiles
all the way up to the radius where the average radial
density reaches the average value.}
For voids with sizes $\reff <8\hMpc$ the outflow is always
positive, consistent with the fact that their density profiles do not
reach the level $\delta=0$ in the range of explored radii.
This behaviour indicates that matter is being pulled out of the void
into external higher density features.

@@

Fig. \ref{fig:FA_profile} shows the results for the FA profiles.
We find that the FA clearly magnifies the difference between the
internal profile $r/\reff <1$ and the external profile $r/\reff >1$. 
Subcompensanted voids in the T-Web reach an asymptotic background
value of F=$0.8$ almost right at $r/\reff =2$. 
For the V-Web the results are similar, albeit rather slowly with the
effective radius.
Overcompensated voids reach a maximum FA at the same effective radiuus
$r/\reff =1$ and decline to reach an asymptotic value of FA=$0.85$
at larger radii.

@@

The difference between the radius where the density ridge is reached 
($r/\reff =3$) and the radius of the FA  ridge ($r/\reff =1$ )
justifies in a more quantiative way the qualitative argument
we present in sub-section \ref{subsec:watershed} to define void boundaries in
our method.  
Namely that as we increase the void boundary, we reach
first middle density walls, before reaching high density structures
associated with high anisotropy. 
This makes the FA ridge a reasonable
boundary for voids compared to the traditional definition that puts
the boundary at the density ridge.

@@

For the density the most interesting feature is that the  profile has
a similar shape for all the different void sizes once the radial
coordinate is expressed in units of the effective radius.  
In these profiles it is evident the presence of an overdense ridge
around $2<r/\reff <3$ for the overcompensated voids.
Subcompensated voids do not show such a ridge keeping its density
lower than the average value up to $r/\reff \sim 8$.

In other studies where voids are found using considerations on the
density fields the ridge is, almost by definition, located around
$r/\reff \sim 1$ and the subcompensated voids reach average
density around $r/\reff \sim 3$. 
This indicates that voids defined by FA boundaries are smaller  than
voids found by density only considerations close by a radial factor of
$2$.

@@

The Fractional Anisotropy profiles also show remarkable similarities
inside each class of subcompensated and overcompensated voids
and a close correlation with the behaviour in the density and velocity
profiles. 
From these profiles it becomes clear that the limit of overcompensated
void coincides with a ridge in of FA values close to $0.9$. 
This value is close to the limit FA=$0.95$ we impose in the watershed
algorithm, indicating that these voids are very close to spherical.
For the subcompensated voids the FA quickly increases to FA values of 
$\sim 0.7-0.8$ at $r/\reff \sim 1$ to find a plateau, which is
quite far from the limiting FA$=0.95$ suggesting that these voids are
far from spherical.
